---
title: "C16, Day 75"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, libraries}
library(harmony)
library(Seurat)
library(cowplot)
library(SCFunctionsV3)
library(dplyr)
library(tidyr)
library(stringr)
library(tidyverse)
library(DoubletFinder)
library(pheatmap)
library(ggplot2)


theme_set(
    theme_classic(base_size = 25)
)


cornea_theme <- cowplot::theme_cowplot() +theme(plot.title = element_text(size=20), 
                                       axis.title.x = element_text(size=20),
                                       axis.title.y = element_text(size=20),
                                       axis.text=element_text(size=18),
                                       axis.text.x= element_text(size = 18, angle = 45, hjust = 1), 
                                       axis.text.y= element_text(size = 18),
                                       #legend.text = element_text(size = 16),
                                       #legend.title=element_text(size=20),
                                       #plot.caption=element_text(size=18), 
                                       #plot.subtitle = element_text(size = 16), 
                                       #axis.ticks = element_blank(), 
                                       strip.text = element_text(size = 0)
                                      )

```


```{r}
#sampleInfo <- readRDS("rObjects/sampleInfo.rds")
seuratObj <- readRDS("rObjects/sObj_Filtered_run2.rds")[[3]]
```



## Annotation 
The clusters were grouped into "conj_superficial"       "epithelial_progenitors" "conj_suprabasal"        "conj_basal"  and "fibroblasts" 

```{r}
plot_cols <- readRDS("rObjects/plot_cols_conjunctiva.rds")

annotations <- read.csv("annotations/D75", sep = ",", header = TRUE)
colnames(annotations) <- c("Cluster", "Annotation")


seuratObj$annotation <- annotations$Annotation[match(seuratObj$RNA_snn_res.1, annotations$Cluster)]

annotations

```



```{r}
DimPlot(seuratObj, 
        group.by = "annotation", 
        cols = plot_cols) + ggsave("highRes/UMAP_annotations_C16_D75.tiff", width = 8, height = 4)

```
## High Res Gene plots

```{r}
genes <- c("krt4",  "muc4", "muc1",
"krt14","tp63", "krt23", "col4a5",
"krt13", "krt19",
"acta2", "COL1A1",
"ace2", "tmprss2", "NC-045512-2") %>% toupper


genes <- intersect(genes, rownames(seuratObj))

gene <- genes[14]
for (i in 1:length(genes)){
  gene <- genes[i]
  
  p1 <- FeaturePlot(seuratObj, features = gene, , 
                    min.cutoff = "q1", 
                    cols = c("#E5E5E5", "#FF0000"), 
                    label = TRUE, order = TRUE, label.size = 2
                    ) + 
    theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size=10))  
    
    p1 + ggsave(paste0("highRes/D75_expression_plot_",                                                                          gene, 
                                                       ".tiff"), 
                                                                         width = 6, height = 4)

  
  
  
}





```

# Percentage of cells in each main group

```{r}
seuratObj$sars_cov2_pos <- seuratObj@assays$RNA@counts["NC-045512-2",] > 0

numberCells <- seuratObj[[]][, c("annotation", "sars_cov2_pos")] %>% 
  group_by(annotation) %>% 
  summarise(number_cells = n(),
            sars_cov2_pos_cells = sum(sars_cov2_pos),
            percentage_cells = n()/dim(seuratObj)[2] * 100
            )

numberCells$percentage_cells_sars_cov2 <- numberCells$sars_cov2_pos_cells / numberCells$number_cells * 100


numberCells %>% write.csv("csvFiles/percentage_cells_c16_C10_C15.csv")

```


# Relative proportion of infected cell types based on expression of viral spike (S) gene



```{r}
exposedCells <- seuratObj[,seuratObj$condition == "positive"][[]][, c("annotation", "sars_cov2_pos")] %>% 
  group_by(annotation) %>% 
  summarise(number_cells = n(),
            sars_cov2_pos_cells = sum(sars_cov2_pos),
            infected = sum(sars_cov2_pos)/n() * 100
            )



exposedCells$uninfected <- 100 - exposedCells$infected

write.csv(exposedCells, "csvFiles/exposedCells.csv")

exposedCells <- gather(exposedCells, 
                       Condition, 
                       percentage_cells, 
                       infected:uninfected)

ggplot(exposedCells, aes(annotation, percentage_cells, fill = Condition)) + geom_bar(stat = "identity") +  theme_minimal() +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +   labs(x = "Cell Type", y = "% cells") +  ggsave("highRes/infected_cell_types.tiff", width = 4, height = 4)
```
# ISG List


```{r}
isg_list <- read.csv("ISG_List", header = FALSE)$V1
isg_list <- list(intersect(isg_list, rownames(seuratObj)))

seuratObj <- AddModuleScore(seuratObj, 
                            features = isg_list, name = "ISG")


seuratObj <- AddModuleScore(seuratObj, 
                            features = isg_list, 
                            name = "ISG_1000_", 
                            ctrl = 200
                            )


isg_list <- read.csv("ISG_List", header = FALSE)$V1
seuratObj$ISG_mean <- colSums(seuratObj@assays$RNA@data[intersect(isg_list, rownames(seuratObj)),])/length(intersect(isg_list, rownames(seuratObj)))



seuratObj$group <- "unexposed"

seuratObj$group[seuratObj$condition == "positive"] <- ifelse(seuratObj$sars_cov2_pos[seuratObj$condition == "positive"], 
                                                             yes = "exposed infected", 
                                                             no = "exposed uninfected")

seuratObj$annotation %>% unique()
p1 <- VlnPlot(seuratObj[,seuratObj$annotation == "conj_superficial"], features = "ISG1",  group.by = "group", pt.size = 0) 
p2 <-VlnPlot(seuratObj[,seuratObj$annotation == "epithelial_progenitors"], features = "ISG1",  group.by = "group", pt.size = 0) 
p3 <- VlnPlot(seuratObj[,seuratObj$annotation == "conj_basal"], features = "ISG1",  group.by = "group", pt.size = 0) 
p4 <- VlnPlot(seuratObj[,seuratObj$annotation == "fibroblasts"], features = "ISG1",  group.by = "group", pt.size = 0) 



p = p1
cellType = "Conj_Superficial"
cols <- c("#2596be", "#862120","#34A488")
avergageBoxPlot <- function(p, cellType){
dat <- p$data
ggplot(dat, aes(ident, ISG1, fill = ident)) + 
   geom_boxplot() +
   theme_minimal() +   labs(x = "Group", 
                            y = "IGS Average Expression") + 
  NoLegend() + 
  ggtitle(cellType) + 
  scale_fill_manual(values = cols)
}



p1b <- avergageBoxPlot(p1, "conj_superficial")
p2b <- avergageBoxPlot(p2, "epithelial_progenitors")
p3b <- avergageBoxPlot(p3, "conj_basal")
p4b <- avergageBoxPlot(p4, "fibroblasts")

p1b + p2b + p3b + p4b +   ggsave("highRes/ISG_boxplot.tiff", width = 8, height = 6)


# Data <- p1$data



# wilcoxonTest <- function(Data, cellType){
#   Data$ISG1 <- log2(Data$ISG1) 
#   #Seperate  Data
#   DataControl<- Data%>%
#                   filter(ident =="unexposed")
#   DataTest <- Data %>%
#     filter(ident == "exposed infected")
#   DataTest2 <- Data %>%
#     filter(ident == "exposed uninfected") 
#   
#   Res1 <- wilcox.test(DataControl$ISG1, DataTest$ISG1, paired = FALSE)$p.value
#   Res2 <- wilcox.test(DataControl$ISG1, DataTest2$ISG1, paired = FALSE)$p.value
#   Res3 <- wilcox.test(DataTest$ISG1, DataTest2$ISG1, paired = FALSE)$p.value
#     #group_by(ident) %>%
#     #summarise(p_value = wilcox.test(DataControl$ISG1, ISG1, exact = FALSE)$p.value )
#   
#   Res <- data.frame(p.value = c(Res1, Res2, Res3),
#              test = c("exposed infected vs unexposed", 
#                       "exposed uninfected vs unexposed", 
#                       "exposed infected vs exposed uninfected"),
#              cellType = cellType)
#   
#   return(Res)
#   
#   }
# 
# 
# 
# ## is the distribution normal?
# qqplot <- function(Data){
#   p <- ggplot(Data, aes(sample = ISG1))
#   p1 <- p + stat_qq() + stat_qq_line() + facet_wrap(~ident)
#   return(p1)
# }
# 
# 
# qqplot(p1$data)
# qqplot(p2$data)
# qqplot(p3$data)
# qqplot(p4$data)
# 
# 
# res <- wilcoxonTest(p1$data, "conj_superficial")
# 
# res <-rbind(res, wilcoxonTest(p2$data, "epithelial_progenitors"))
# res <-rbind(res, wilcoxonTest(p3$data, "conj_basal"))
# res <-rbind(res, wilcoxonTest(p4$data, "fibroblasts"))
# 
# 
# res$p.value.adjust <- p.adjust(res$p.value)
# 
# res$significant <- res$p.value.adjust < 0.05 
# 
# 
# write.csv(res, )
```

## Heatmap of ISG expression

```{r}
isg_list_short <- read.csv("ISG_List", header = FALSE)$V1

isg_list_short <- intersect(isg_list_short, rownames(seuratObj@assays$RNA@scale.data))

tmp <- seuratObj@assays$RNA@scale.data[isg_list_short,]

tmp <- tmp %>% data.frame() %>%  t() %>% data.frame()



positive_negative <- ifelse(seuratObj@assays$RNA@counts["NC-045512-2",] > 0, 
                            yes = "infected", 
                            no = "uninfected")


infected_uninfected <- ifelse(seuratObj$condition == "positive" , yes = "exposed", no = "unexposed")

seuratObj$groups <- paste(infected_uninfected, positive_negative, sep = "_")
tmp$group <- seuratObj$groups
tmp$annotation <- seuratObj$annotation
tmp$annotation_group <- paste(tmp$group, 
                              tmp$annotation, 
                              sep = "_")

data_long <- gather(tmp, gene, expression, isg_list_short)
data_long$group <- gsub("unexposed_uninfected", "unexposed", data_long$group)
data_long$group <- gsub("_", ",", data_long$group)

p1 <- ggplot(data_long, aes(gene, group, fill = expression)) + 
  geom_tile() +
  scale_fill_steps2(
  low = "#00eaff",
  high = "#ff0000",
  mid = "white", 
  midpoint = 0) + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  facet_wrap(~annotation, ncol = 1) + labs(x = "", y = "")

p1 + ggsave("highRes/ISG_heatmap.tiff", width = 12, height = 6)

```

## Dot plot of differentially-expressed IFNs

```{r}
seuratObj$clusters <- seuratObj@active.ident
seuratObj <- SetIdent(seuratObj, value = "annotation")

markers <- FindAllMarkers(seuratObj, only.pos = TRUE)
DE_list <- list.files("csvFiles/DE_Lists_conjunctiva_files_moved/", pattern = "vs")

markers_IFN <- markers[grepl("IFN", markers$gene), ]

markers_IFN %>%  write.csv("csvFiles/markers_IFNs.csv")

gene_list <- markers$gene[grepl("IFN", markers$gene)] %>% unique()
p2 <- DotPlot(seuratObj, 
              features = rev(gene_list), 
              cols = c("blue", "red"), 
              col.min = 0, 
              col.max = 2.5,
              group.by = "annotation_group") 



p2$data %>%  
  dplyr::filter(pct.exp > 0 ) %>%   
  ggplot(aes(x= features.plot, y = id, color = avg.exp.scaled, size = pct.exp)) + 
  geom_point() +
  ylab('') +
  xlab('') + 
  scale_colour_gradient(low = "blue", high = "red") + 
  cornea_theme +
  scale_radius(range = c(0, 5)) +  
  # ggsave("SarsCov2_Figures/entrty_factors.tiff", width = 35, height = 20, units = "cm", dpi = 300) +
  ggsave("highRes/DE_IFNs.tiff", width = 43, height = 20, units = "cm", dpi = 300)

p2$data %>% write.csv("csvFiles/DE_IFNs.csv")

```

## dot plot NF-KB

```{r}
gene_list <- read.csv("csvFiles/NF-KB", header = FALSE)$V1


p2 <- DotPlot(seuratObj, 
              features = rev(gene_list), 
              cols = c("blue", "red"), 
              col.min = 0, 
              col.max = 2.5,
              group.by = "annotation_group") 



p2$data %>%  
  dplyr::filter(pct.exp > 0 ) %>%   
  ggplot(aes(x= features.plot, y = id, color = avg.exp.scaled, size = pct.exp)) + 
  geom_point() +
  ylab('') +
  xlab('') + 
  scale_colour_gradient(low = "blue", high = "red") + 
  cornea_theme +
  scale_radius(range = c(0, 5)) +  
  # ggsave("SarsCov2_Figures/entrty_factors.tiff", width = 35, height = 20, units = "cm", dpi = 300) +
  ggsave("highRes/NF-KB.tiff", width = 43, height = 20, units = "cm", dpi = 300)

p2$data %>% write.csv("csvFiles/NF-KB.csv")



```

## dot plot 


```{r}
gene_list <- read.csv("csvFiles/virus_stimulated_genes", header = FALSE)$V1


p2 <- DotPlot(seuratObj, 
              features = gene_list, 
              cols = c("blue", "red"), 
              col.min = 0, 
              col.max = 2.5,
              group.by = "annotation_group") 


seuratObj$condition_cellType <- paste(seuratObj$condition, seuratObj$annotation)
DotPlot(seuratObj, 
              features = gene_list, 
              cols = c("blue", "red"), 
              col.min = 0, 
              col.max = 2.5,
              group.by = "condition_cellType") 

p2$data %>%  
  dplyr::filter(pct.exp > 0 ) %>%   
  ggplot(aes(x= features.plot, y = id, color = avg.exp.scaled, size = pct.exp)) + 
  geom_point() +
  ylab('') +
  xlab('') + 
  scale_colour_gradient(low = "blue", high = "red") + 
  cornea_theme +
  scale_radius(range = c(0, 5)) +  
  # ggsave("SarsCov2_Figures/entrty_factors.tiff", width = 35, height = 20, units = "cm", dpi = 300) +
  ggsave("highRes/virus_stimulated.tiff", width = 43, height = 20, units = "cm", dpi = 300)

p2$data %>% write.csv("csvFiles/virus_stimulated.csv")



```

```{r, eval = FALSE}
saveRDS(seuratObj, "rObjects/seuratObj_C16_C10_C15_D33.rds")
```




```{r}
data("pbmc_small")
cd_features <- list(c(
  'CD79B',
  'CD79A',
  'CD19',
  'CD180',
  'CD200',
  'CD3D',
  'CD2',
  'CD3E',
  'CD7',
  'CD8A',
  'CD14',
  'CD1C',
  'CD68',
  'CD9',
  'CD247'
))
pbmc_small <- AddModuleScore(
  object = pbmc_small,
  features = cd_features,
  ctrl = 5,
  name = 'CD_Features'
)
```



# Gene Plots


```{r}
genes <- c("krt7", "krt13", "s100a8",  "s100a9", "krt6a", "krt14", "krt15", "muc1", "muc4", "krt4", "krt12", "krt3", "lypd2", "hes1", "hes5", "krt24", "areg", "COL1A1", "fbln1", "col1a3", "kera", "lum", "mmp3", "tagln", "acta2", "tp63", "ace2", "tmprss2", "Mki67", "CDH19", "CCL21", "LYVE1", "POSTN", "isg15", "rsad2", "NC-045512-2") %>% toupper()
```


```{r}
plotGenes <- function(sObj, geneList){
  sampleName <- as.character(unique(sObj$orig.ident))
  geneList <- intersect(geneList, rownames(sObj))
  p_list <- list()
    for (gene in geneList){
      p1 <- FeaturePlot(sObj, features = gene, 
                        min.cutoff = "q1", 
                        cols = c("#E5E5E5", "#FF0000"), 
                        label = TRUE, order = TRUE, label.size = 2
                        ) +
        theme(panel.grid = element_blank(),
            axis.title = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank(),
            text = element_text(size=10)) 
        
      p1
      p_list[[gene]] <- p1
    
    }
  
  return(p_list)
}

p_list <- plotGenes(seuratObj, geneList = genes)


p_list


```

## Numbers of Cells

```{r, fig.height = 30, fig.width= 15}
number_cells_by_stage <- seuratObj[[]] %>% select(c("tissue", "RNA_snn_res.2.2")) %>% group_by(tissue) %>% summarise(number_cells_by_sample = n())

number_cells <- seuratObj[[]] %>% select(c("tissue", "RNA_snn_res.2.2")) %>% group_by(tissue,RNA_snn_res.2.2) %>% summarise(number_cells = n()) %>% left_join(number_cells_by_stage)


number_cells$normalised_cell_number <- number_cells$number_cells /number_cells$number_cells_by_sample * 100


number_cells <- number_cells %>% select(c("tissue", "RNA_snn_res.2.2", "normalised_cell_number")) %>% group_by(RNA_snn_res.2.2) %>% summarise(cluster_total = sum(normalised_cell_number)) %>% right_join(number_cells)




number_cells$percentage <- number_cells$normalised_cell_number / number_cells$cluster_total * 100


number_cells %>% 
  ggplot(aes(tissue, percentage, fill = tissue)) + 
  geom_bar(stat =  "identity") + 
  facet_wrap(~RNA_snn_res.2.2, nrow = 14, scales = "free", drop = FALSE) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 



```

# percentage of ace2pos tmprss2 pos co-expressing cells

36% of cells co-express ace2 and tmprss

```{r}
total_cells <- dim(seuratObj)[2]

ACE2_TMPRSS2Pos <- seuratObj@assays$RNA@counts["ACE2",] > 0 & 
seuratObj@assays$RNA@counts["TMPRSS2",] > 0


sum(ACE2_TMPRSS2Pos) / total_cells * 100
```



