---
title: "C16, C1O, C15 Day 33 Integration, all samples"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, libraries}
library(harmony)
library(Seurat)
library(cowplot)
library(SCFunctionsV3)
library(dplyr)
library(tidyr)
library(stringr)
library(tidyverse)
library(DoubletFinder)
library(pheatmap)
library(ggplot2)
```


```{r}
#sampleInfo <- readRDS("rObjects/sampleInfo.rds")
seuratObj <- readRDS("rObjects/seuratObj_C16_C10_C15_D33.rds")
seuratObj$sample <- paste(seuratObj$cell_line, seuratObj$condition, sep = "_")
```

# Samples Integrated

C16	Conjunctiva	33 negative
C16	Conjunctiva	33 positive
C15	Conjunctiva	33 negative
C15	Conjunctiva	33 positive
C10	Conjunctiva	33 negative
C10	Conjunctiva	33 positive

```{r, eval = FALSE}
# 5_integrate_conjunctiva.R
```

There were small technical differences between the number of counts and number of genes and percentage mitochondria between the three samples. These factors were regressed out.

```{r}
VlnPlot(seuratObj, 
        group.by = "sample", 
        features = c("nCount_RNA", 
                     "nFeature_RNA", 
                     "percent.mt"), 
        pt.size = 0)
```


```{r, harmony, eval = FALSE}
# 5_integrate_conjunctiva.R
```


## Integrated data

Differences between the samples are seen after integration.

```{r, fig.width=25, fig.height = 15}



#p0 <- DimPlot(seuratObj)
p1 <- DimPlot(seuratObj, group.by = "sample")
p2 <- DimPlot(seuratObj, group.by = "Phase")


p1 + p2 

```

## Clusters

```{r, fig.width=25, fig.height = 15}
p0 <- DimPlot(seuratObj, label = TRUE)

p0 
```


# Gene Plots

```{r}
genes <- c("krt7", "krt13", "s100a8",  "s100a9", "krt6a", "krt14", "krt15", "muc1", "muc4", "krt4", "krt12", "krt3", "lypd2", "hes1", "hes5", "krt24", "areg", "COL1A1", "fbln1", "col1a3", "kera", "lum", "mmp3", "tagln", "acta2", "tp63", "ace2", "tmprss2", "Mki67", "CDH19", "CCL21", "LYVE1", "POSTN", "isg15", "rsad2") %>% toupper()


covid_genes <- readRDS("rObjects/covid_genes.rds")

genes <- c(genes, covid_genes)

```


```{r}
plotGenes <- function(sObj, geneList){
  sampleName <- as.character(unique(sObj$orig.ident))
  geneList <- intersect(geneList, rownames(sObj))
  p_list <- list()
    for (gene in geneList){
      p1 <- FeaturePlot(sObj, features = gene, 
                        min.cutoff = "q1", 
                        cols = c("#E5E5E5", "#FF0000"), 
                        label = TRUE, order = TRUE, label.size = 2
                        ) +
        theme(panel.grid = element_blank(),
            axis.title = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank(),
            text = element_text(size=10)) 
        
      p1
      p_list[[gene]] <- p1
    
    }
  
  return(p_list)
}

p_list <- plotGenes(seuratObj, geneList = genes)


p_list


```


## Numbers of Cells

```{r, fig.height = 30, fig.width= 15}
number_cells_by_stage <- seuratObj[[]] %>% select(c("sample", "RNA_snn_res.2.2")) %>% group_by(sample) %>% summarise(number_cells_by_sample = n())

number_cells <- seuratObj[[]] %>% select(c("sample", "RNA_snn_res.2.2")) %>% group_by(sample,RNA_snn_res.2.2) %>% summarise(number_cells = n()) %>% left_join(number_cells_by_stage)


number_cells$normalised_cell_number <- number_cells$number_cells /number_cells$number_cells_by_sample * 100


number_cells <- number_cells %>% select(c("sample", "RNA_snn_res.2.2", "normalised_cell_number")) %>% group_by(RNA_snn_res.2.2) %>% summarise(cluster_total = sum(normalised_cell_number)) %>% right_join(number_cells)




number_cells$percentage <- number_cells$normalised_cell_number / number_cells$cluster_total * 100


number_cells %>% 
  ggplot(aes(sample, percentage, fill = sample)) + 
  geom_bar(stat =  "identity") + 
  facet_wrap(~RNA_snn_res.2.2, nrow = 14, scales = "free", drop = FALSE) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 



```

# TO DO!!
## Annotation 
The clusters were grouped into "conj_superficial"       "epithelial_progenitors" "conj_suprabasal"        "conj_basal"  and "fibroblasts" 

```{r, eval = FALSE}


annotations <- read.csv("conjunctiva_labels_negative.txt", sep = ":", header = FALSE)
colnames(annotations) <- c("Cluster", "Annotation", "Genes")
annotations$Genes <- annotations$Genes %>% toupper


seuratObj$annotation <- annotations$Annotation[match(seuratObj$RNA_snn_res.2.2, annotations$Cluster)]

annotations


plot_cols <- c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00')
names(plot_cols) <- annotations$Annotation %>% unique()
saveRDS(plot_cols, "rObjects/plot_cols_conjunctiva.rds")


DimPlot(seuratObj, group.by = "annotation", cols = plot_cols) + ggsave("highRes/UMAP_annotations_C16_C10_C15_negative.tiff", width = 8, height = 4)

```

# TO DO!!
## High Res Gene plots

```{r, eval = FALSE}
genes <- c("krt4",  "muc4", "muc1",
"krt14","tp63", "krt23", "col4a5",
"krt13", "krt19",
"acta2", "COL1A1",
"ace2", "tmprss2") %>% toupper


gene <- genes[1]
for (i in 1:length(genes)){
  gene <- genes[i]
  
  p1 <- FeaturePlot(seuratObj, features = gene, , 
                    min.cutoff = "q1", 
                    cols = c("#E5E5E5", "#FF0000"), 
                    label = TRUE, order = TRUE, label.size = 2
                    ) + 
    theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size=10))  
    
    p1 + ggsave(paste0("highRes/expression_plot_",                                                                          gene, 
                                                       "_C16_C10_C15_negative.tiff"), 
                                                                         width = 6, height = 4)

  
  
  
}





```

# TO DO!!
# Percentage of cells in each main group - 

```{r, eval = FALSE}
numberCells <- seuratObj[[]][, "annotation", drop = FALSE] %>% 
  group_by(annotation) %>% 
  summarise(number_cells = n(),
            percentage_cells = n()/dim(seuratObj)[2] * 100) %>% write.csv("csvFiles/percentage_cells_c16_C10_C15_negative.csv")

```







