---
title: "NFKB boxplot"
output: html_notebook
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
library(Seurat)
library(ggplot2)
library(dplyr)
library(SCFunctionsV3)
library(ggplot2)
library(dplyr)
library(cowplot)
```

```{r}
theme_set(
    theme_classic(base_size = 25)
)


cornea_theme <- cowplot::theme_cowplot() +theme(plot.title = element_text(size=20), 
                                       axis.title.x = element_text(size=20),
                                       axis.title.y = element_text(size=20),
                                       axis.text=element_text(size=18),
                                       axis.text.x= element_text(size = 18, angle = 45, hjust = 1), 
                                       axis.text.y= element_text(size = 18),
                                       #legend.text = element_text(size = 16),
                                       #legend.title=element_text(size=20),
                                       #plot.caption=element_text(size=18), 
                                       #plot.subtitle = element_text(size = 16), 
                                       #axis.ticks = element_blank(), 
                                       strip.text = element_text(size = 0)
                                      )
```

```{r}
#sampleInfo <- readRDS("rObjects/sampleInfo.rds")
seuratObj <- readRDS("rObjects/seuratObj_C16_C10_C15_D33.rds")
annotations <- read.csv("annotations/infected_unininfected.csv")[,2:3]
colnames(annotations) <- c("Cluster", "Annotation")
annotations$Cluster <- factor(annotations$Cluster)

seuratObj$annotation <- annotations$Annotation[match(seuratObj$RNA_snn_res.2.2, annotations$Cluster)]

annotations


plot_cols <- c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00')
names(plot_cols) <- annotations$Annotation %>% unique()
#saveRDS(plot_cols, "rObjects/plot_cols_conjunctiva.rds")

``` 

## NFKB boxplot

```{r}
NFKB_list <- read.csv("csvFiles/NFKB_targets.csv", header = FALSE)$V1

setdiff(NFKB_list, rownames(seuratObj@assays$RNA@counts))


NFKB_list <- intersect(NFKB_list, rownames(seuratObj@assays$RNA@counts)) %>% list()

seuratObj <- AddModuleScore(seuratObj, 
                            features = NFKB_list, 
                            name = "NFKB_score")





#seuratObj$annotation %>% unique()
p1 <- VlnPlot(seuratObj[,seuratObj$annotation == "superficial conjunctival epithelium"], features = "NFKB_score1",  group.by = "group", pt.size = 0) 
p2 <-VlnPlot(seuratObj[,seuratObj$annotation == "conjunctival epithelial progenitors"], features = "NFKB_score1",  group.by = "group", pt.size = 0) 
p3 <- VlnPlot(seuratObj[,seuratObj$annotation == "basal conjunctival epithelium"], features = "NFKB_score1",  group.by = "group", pt.size = 0) 
p4 <- VlnPlot(seuratObj[,seuratObj$annotation == "fibroblasts"], features = "NFKB_score1",  group.by = "group", pt.size = 0) 



p = p1
cellType = "superficial conjunctival epithelium"
cols <- c("#2596be", "#862120","#34A488")
avergageBoxPlot <- function(p, cellType){
dat <- p$data
ggplot(dat, aes(ident, NFKB_score1, fill = ident)) + 
   geom_boxplot() +
   theme_minimal() +   labs(x = "Group", 
                            y = "NFKB Average Expression") + 
  NoLegend() + 
  ggtitle(cellType) + 
  scale_fill_manual(values = cols)
}



p1b <- avergageBoxPlot(p1, "Superficial conjunctival epithelium")
p2b <- avergageBoxPlot(p2, "Conjunctival epithelial progenitors")
p3b <- avergageBoxPlot(p3, "Basal conjunctival epithelium")
p4b <- avergageBoxPlot(p4, "Fibroblasts")

p1b + p2b + p3b + p4b +   ggsave("highRes/NFKB_boxplot.tiff", width = 8, height = 6)

# p1b + p2b + p3b + p4b +   ggsave("highRes/ISG_boxplot.png", width = 8, height = 6)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
