---
title: "Compare with Adult cornea"
output:
  html_document:
    df_print: paged
---


I combined the conjuntival organoids with adult cornea using a standard harmony batch correction. I combined the organoids with:

1. All the whole cornea dataset  
2. Clusters 0 and 6
3. Clusters 0,6 and 9

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
library(Seurat)
library(ggplot2)
library(dplyr)
library(SCFunctionsV3)
library(ggplot2)
library(dplyr)
library(cowplot)

seuratObj_C16_C10_C15_D33 <- readRDS("/data/rachel/Linda_Lako/Covid_SC/Repeat/rObjects/seuratObj_C16_C10_C15_D33.rds")

seuratAdult <- readRDS("/data/rachel/Linda_Lako/Cornea/Adult_Cornea/rObjects/Combined.rds")
## processed compare_with_cornea.R
seurat_all <- readRDS("rObjects/cornea_comparison_all.rds")
seurat_0_6 <- readRDS("rObjects/cornea_comparison_0_6.rds")
seurat_0_6_9 <- readRDS("rObjects/cornea_comparison_0_6_9.rds")
seurat_superficial_0_6 <- readRDS("rObjects/cornea_comparison_superficial_0_6.rds")
seurat_superficial <- readRDS("rObjects/cornea_comparison_superficial_6.rds")
seurat_basal_0_6 <- readRDS("rObjects/cornea_comparison_basal_0_6.rds")
seurat_basal <- readRDS("rObjects/cornea_comparison_basal_0.rds")


plotCols1 <- c(readRDS("/data/rachel/Linda_Lako/Cornea/Adult_Cornea/rObjects/plotCols21.rds"))


plotCols2 <- readRDS("rObjects/plot_cols_conjunctiva.rds")
names(plotCols2) <- c("basal conjunctival epithelium", "conjunctival epithelial progenitors", "fibroblasts", "superficial conjunctival epithelium")


plotCols <- c(plotCols1, plotCols2)
plotCols <- plotCols[levels(factor(seurat_all$cellType))]
```



## Cornea
```{r}
p0 <- DimPlot(seuratAdult, cols = plotCols1, pt.size = 1.5, label = TRUE)
```


## All cells


```{r}
DimPlot(seurat_all,  group.by = "tissue", label = TRUE, pt.size = 1.5)
```


```{r, fig.width = 20}
p0 + DimPlot(seurat_all,  group.by = "cellType", split.by = "tissue", label = TRUE, cols = plotCols, pt.size = 1.5) 
```




```{r, fig.width = 20, eval = FALSE}

## Subset 

#The combined data was subset to just show conjunctival cells
p <- DimPlot(seurat_all[,seurat_all$tissue == "Adult Cornea"], cols = plotCols1, pt.size = 1.5, label = TRUE)


seurat_subset <- seurat_all[,seurat_all$cellType %in% c("0", "basal conjunctival epithelium")]
p + DimPlot(seurat_subset,  group.by = "cellType",  label = TRUE, cols = plotCols, pt.size = 1.5) 
seurat_subset <- seurat_all[,seurat_all$cellType %in% c("6", "basal conjunctival epithelium")]
p + DimPlot(seurat_subset,  group.by = "cellType",  label = TRUE, cols = plotCols, pt.size = 1.5) 


seurat_subset <- seurat_all[,seurat_all$cellType %in% c("6", "superficial conjunctival epithelium")]
p0 + DimPlot(seurat_subset,  group.by = "cellType",  label = TRUE, cols = plotCols, pt.size = 1.5) 
seurat_subset <- seurat_all[,seurat_all$cellType %in% c("0", "superficial conjunctival epithelium")]
p0 + DimPlot(seurat_subset,  group.by = "cellType",  label = TRUE, cols = plotCols, pt.size = 1.5)


```

## Cluster 0, 6
```{r}
DimPlot(seurat_0_6,  group.by = "tissue", label = TRUE, pt.size = 1.5)
```

```{r,  fig.width = 20}
p0 + DimPlot(seurat_0_6,  group.by = "cellType", split.by = "tissue", label = TRUE, cols = plotCols, pt.size = 1.5) 
```


## Cluster 0, 6, 9

```{r}
DimPlot(seurat_0_6_9,  group.by = "tissue", label = TRUE, pt.size = 1.5)
```


```{r, fig.width = 20}
p0 + DimPlot(seurat_0_6_9,  group.by = "cellType", split.by = "tissue", label = TRUE, cols = plotCols, pt.size = 1.5) 
```



## Comparison of basal conjunctiva

```{r, fig.width = 20}
DimPlot(seurat_basal,  group.by = "cellType", label = TRUE, cols = plotCols, pt.size = 1.5)
DimPlot(seurat_basal_0_6,  group.by = "cellType", label = TRUE, cols = plotCols, pt.size = 1.5) 
```
## Comparison of superficial conjunctiva

```{r, fig.width = 20}
DimPlot(seurat_superficial,  group.by = "cellType", label = TRUE, cols = plotCols, pt.size = 1.5)
DimPlot(seurat_superficial_0_6,  group.by = "cellType", label = TRUE, cols = plotCols, pt.size = 1.5) 
```



The correlation of expression of the top 2000 highly variable genes between each of the ALI organoid cell type and the 21 adult cornea clusters was calculated (cluster_correlations.csv)


```{r, eval = FALSE}

df <- seurat_all@assays$RNA@data[VariableFeatures(seuratAdult),] %>% data.frame() %>% t() %>% data.frame()
df$cluster <- seurat_all$cellType
avgExpression <- df %>% 
  group_by(cluster) %>% 
  summarise_all(mean) %>%
  as.data.frame() %>% 
  tibble::remove_rownames() %>%
  tibble::column_to_rownames("cluster")


cluster1 <- seuratObj_C16_C10_C15_D33$annotation %>% unique() %>% rep(each = 21)


comparisons <- data.frame(cluster1 = cluster1,
                 cluster2 = as.character(rep(c(0:20), 4)), stringsAsFactors = FALSE)
comparisons$correlation_coefficient <- 0


for (i in 1:nrow(comparisons)){
  comparisons$correlation_coefficient[i] <- cor(unname(unlist(avgExpression[comparisons$cluster1[i], ])), 
    unname(unlist(avgExpression[comparisons$cluster2[i],])))
  
  
}

comparisons %>% arrange(cluster1, desc(correlation_coefficient)) %>% write.csv("csvFiles/cluster_correlations.csv", row.names = FALSE, quote = FALSE)





```





